Software Citation Principles

### 2016-05-09 sc-principles/software-citation-principles.tex
fixing grammar in the importance principle as suggested by Maryann Martone through Hypothesis

\begin{enumerate}
\item \textbf{Importance}: \label{principle:importance} Software should be
considered a legitimate and citable product of research. Software citations should
be accorded the same importance in the scholarly record as citations of other
research products, such as publications and data; they should be included in the
metadata of the citing work, for example in the reference list of a journal article,
and should not be omitted or separated.
Software should be cited on the same basis as any other research products such as
papers or books, that is, authors should cite the appropriate set of software
products just as they cite the appropriate set of papers.

@@

The goals of software include the linked ideas of crediting those responsible for software and understanding the dependencies of research products on specific software.
In the Importance principle~(\ref{principle:importance}), we state that
``software should be cited on the same basis as any other research product such as a paper or book; that is, authors should cite the appropriate set of software products just as they cite the appropriate set of papers.''
In the case of one code that is derived from another code, citing the derived software may appear to not credit those responsible for the original software, nor recognize its role in the work that used the derived software.
However, this is really analogous to how any research builds on other research, where each research product just cites those products that it directly builds on, not those that it indirectly builds on.
Understanding these chains of knowledge and credit have been part of the history of science field for some time, though more recent work is suggesting more nuanced evaluation of the credit chains~\cite{casrai-credit, transitive_credit_json-ld}.

>>>>

\begin{enumerate}
\item \textbf{Importance}: \label{principle:importance} Software should be
considered a legitimate and citable product of research. Software citations should
be accorded the same importance in the scholarly record as citations of other
research products, such as publications and data; they should be included in the
metadata of the citing work, for example in the reference list of a journal article,
and should not be omitted or separated.
Software should be cited on the same basis as any other research product such as
a paper or a book, that is, authors should cite the appropriate set of software
products just as they cite the appropriate set of papers.

@@

The goals of software include the linked ideas of crediting those responsible for software and understanding the dependencies of research products on specific software.
In the Importance principle~(\ref{principle:importance}), we state that
``software should be cited on the same basis as any other research product such as a paper or a book; that is, authors should cite the appropriate set of software products just as they cite the appropriate set of papers.''
In the case of one code that is derived from another code, citing the derived software may appear to not credit those responsible for the original software, nor recognize its role in the work that used the derived software.
However, this is really analogous to how any research builds on other research, where each research product just cites those products that it directly builds on, not those that it indirectly builds on.
Understanding these chains of knowledge and credit have been part of the history of science field for some time, though more recent work is suggesting more nuanced evaluation of the credit chains~\cite{casrai-credit, transitive_credit_json-ld}.
